---
title: "Effects of Initial Curiosity and Prediction Error on Explicit and Incidental Memory Formation"
authors: "Cherrie Chang, Amaavi Miriyagalla, Jasmine Shao"
format: html
editor: visual
---

```{r}
#| label: Load R libraries
#| echo: false
#| message: false

library(osfr)
library(readr)
library(dplyr)
library(ggplot2)
library(ez)
```

```{r}
#| label: Retrieve the data from OSF
#| echo: false
#| include: false

osf_retrieve_node("ubnxa") %>%
  osf_ls_files() %>%
  osf_download(path = "data/", conflicts = "skip")
```

```{r}
#| label: Convert Files from JSON to CSV
#| echo: false
#| include: false

files <- list.files("data") %>%
  data <- lapply(files, fromJSON) %>%
  bind_rows()
```

## Introduction

## Methods

```{r}
#| label: Load the Data
#| message: false
#| echo: false

behavioral.data <- read.csv('data/behavioral.csv')
```

```{r}
#| label: Count the Number of Subjects
#| echo: false

n.subjects <- behavioral.data %>%
  pull(subject) %>%
  unique() %>%
  length()
```

### Pre-Registration & Open Materials

All stimuli, experiment scripts, data, and analysis scripts are available on the Open Science Framework at <https://osf.io/v35df/>. The pre-registration for this study is also available at <https://osf.io/w3qh4>. This study was approved by the Vassar College Institutional Review Board, and all participants provided informed consent prior to their participation.

### Participants

### Procedure

## Results

```{r}
#| label: Summarize behavioral data
#| message: false
#| echo: false

behavioral.summary <- behavioral.data %>%
  group_by() %>%
  summarise()
```

```{r}
#| label: Exclude Subjects Who Got >20 Questions Correct in the Initial Round
#| message: false
#| echo: false


```

```{r}
#| label: Exclude Subjects Who Do Not Have Variable Responses to Write-in/Scale Questions
#| message: false
#| echo: false

```

### Z-Scores

```{r}
#| label: Prediction Error Z-Scores (each participant AND each question)
#| message: false
#| echo: false
```

```{r}
#| label: Curiosity Z-Scores (each participant)
#| message: false
#| echo: false
```

### Regressions

```{r}
#| label: Explicit Memory Regression
#| message: false
#| echo: false
```

```{r}
#| label: Incidental Memory Regression
#| message: false
#| echo: false
```

## Discussion

## References

Cervera, R. L., Wang, M. Z., & Hayden, B. Y. (2020). Systems neuroscience of curiosity. Current Opinion in Behavioral Sciences, 35, 48--55. https://doi.org/10.1016/j.cobeha. 2020.06.011

Fernández, R. S., Boccia, M. M., & Pedreira, M. E. (2016). The fate of memory: Reconsolidation and the case of prediction error. Neuroscience & Biobehavioral Reviews, 68, 423--441. https://doi.org/10.1016/j.neubiorev.2016.06.004

Gruber, M. J., Gelman, B. D., & Ranganath, C. (2014). States of curiosity modulate hippocampus-dependent learning via the dopaminergic circuit. Neuron, 84(2), 486--496. https://doi.org/10.1016/j.neuron.2014.08.060

Kang, M. J., Hsu, M., Krajbich, I. M., Loewenstein, G., McClure, S. M., Wang, J. T., & Camerer, C. F. (2009). The Wick in the Candle of Learning: Epistemic Curiosity Activates Reward Circuitry and Enhances Memory. Psychological Science, 20(8), 963--973. https://doi.org/10.1111/j.1467-9280.2009.02402

van Lieshout, L. L. F., de Lange, F. P., & Cools, R. (2020). Why so curious? quantifying mechanisms of information seeking. Current Opinion in Behavioral Sciences, 35, 112--117. https://doi.org/10.1016/j.cobeha.2020.08.005

Wade, S., & Kidd, C. (2019). The role of prior knowledge and curiosity in learning. Psychonomic Bulletin & Review, 26(4), 1377--1387. https://doi.org/10.3758/s13423 -019-01598-6
